\chapter{Introduction}

\section{Motivation}
\par The sports industry in North America alone currently is worth 60.5 billion dollars and this industry has been projected to grow to 73.5 billion dollars by 2019. This rise in projected growth happens due to the fact that media companies are making larger deals, which in turn is caused by more people being entertained by sports. However, not everyone can make it to the television for every game, and not everyone has the time to watch a full-length game. This creates the need for easy access to fast sports highlights and other sports statistics that can help individuals relive the exciting moments in a match/game without having to spend too much of their time watching the actual event. Therefore, a user should be able to navigate to a website and within a few seconds be watching the game he or she intended to watch. Quite a few of these websites currently exist today, but we think that they could be dramatically improved.\par
There are many websites today that have attempted to solve this issue, but while attempting to cover all sports related issues, they have gotten away from the simple goal of highlighting sports in a precise fashion. Websites like ESPN.com, FoxSports.com, and BleacherReport.com all encompass some of the highlights from a particular sport’s league, but they all have become cluttered with loosely related sports articles and irrelevant game interviews. The current methods include too many articles, and these articles often take up too much space within a user’s window. This is troublesome because the user should simply get to the video highlights in a fast manner, without having to traverse the entire cluttered site for over 30 seconds; the search time must be decreased. In addition to that, when it comes to different sports, the current implementation does not have any continuity between the sports; in other words, the view for soccer typically varies significantly from the view for basketball. Website usability is key for user experience because discontinuity between key pages can lead to frustrations causing a user to discontinue use of a website. Lastly, many current implementations do not have a reliable source of efficient highlights. For example, some websites will leave out certain games within a league, creating an inconvenience for the user who is just trying to view his or her desired highlight.


\section{Solution}

\par Our solution is to use modern technologies in order to create a simple, centralized web application in which users can easily view any highlight within any sport and league. We will make sure there is continuity between different sports pages by using a one-size fit all view. In addition to that, there will be unique customization features, so highlights can be catered to users’ interests. The system will pull videos and gifs with thorough content ensuring fans can experience a full game in a matter of minutes, and we can will guarantee no game within a season is missing. The window for viewing video will be conveniently placed in the middle of the website, making it easier for people to see, with navigation bars around that centralized feature. We will not include articles because that takes away from the viewing experience and makes it harder to search for highlights in a timely manner. Overall, the different, more simple user experience along with more unique customization and guaranteed highlights will provide users who are interested in highlights the ideal platform for them to follow their teams and games. 

