\begin{abstract}
%A good abstract is a concise summary (1--2 paragraphs) of the entire
%project: introduction, problem statement, work accomplished, results,
%conclusions, and recommendations. When you write the abstract, imagine
%that the reader will not read anything else, but that you must get
%your major point across immediately. This requires efficiency of words
%and phrases. An abstract is written to stand alone, without jargon or
%eference to figures and tables in the report body.
\doublespacing
\par The sports sector has experienced major growth over the past couple of decades and is anticipated to grow even faster in the foreseeable future, especially as media technology continues to advance and access to sports games continues to increase. As the audience of sports enthusiast and observers expands, more people may miss the most recent and interesting sporting events from the previous night. Many websites have attempted to serve these groups, but they have become cluttered with articles or short-clips that hold little to no significance to the sporting outcome. These websites have begun  to get away from the simple need of highlighting an event in an efficient format. Our solution, Shot Clock, is a simple, centralized web application to view sports highlights that functions by taking advantage of today's modern technologies. The web application will also provide a user experience that promotes simplicity, continuity, and ease of use when navigating the application. Users will also have the opportunity to create custom lists so that they can be kept up to date to their favorite teams. Succeeding in these major facets will provide audiences with the practicality of easy access to precise replays delivering an innovative experience that users will appreciate.

\end{abstract}
