\chapter{Test Plan}

\section{Unit Testing}
Unit testing of our website will be useful in the preliminary stages of testing. This form of testing can be done to ensure that we have correct functionality of individual features. The focus of this testing will be to ensure our web crawler grabs the data we specified it to. The database we decide to use will also be tested to ensure it can hold a high amount data entries as well as be reliable to grab entries efficiently. Lastly, our webpage will be thoroughly tested to ensure the integrity of the aesthetics is kept among several browsers and operating systems.

\section{Integration Testing}
The integration testing of our program will be one of the most crucial steps. During this testing phase we will begin connecting services and functionality to ensure that the program can function as a whole. Components will be pieced together one at a time so that the errors can be pinpointed and the problem can be specified. As each service is connected to the completed system the errors will become obvious as to which portion of the project is improperly functioning.  

\section{Alpha Testing}
Alpha testing will be completed in-house by our team once integration testing is complete. During alpha testing we can test the completed system functionality as the product will be near completion and fully functional. As the system is tested, we will find the bugs and errors that are still prevalent in the code causing erroneous results. Along with catching the bugs in the program, we will also be able to ensure that all requirements are being satisfied by the system. 

\section{Beta Testing}
During beta testing we will expand testing from only group members to friends, colleagues, or others interested in the project. By this step most user cases should be thoroughly tested and functional. We will use tester feedback to improve the user-interface aspects that are generally agreed upon. As some bugs will be still uncaught before this process, using beta testers will ensure that all possible situations are exhausted and that the program is ready to be used.
