\chapter{Societal Issues}

\section{Introduction}
\par In any engineering project, there are many different social issues that could and should be taken into account. We initially knew some of the issues that we would encounter as we moved forward, and as we began to actually develop our project further and further, we thought of more and more issues that we needed to consider and take into account. 

\section{Ethical}
\par We faced a little bit of ethical dilemmas as we proceeded to work on our project. First and foremost, we recognized that since we needed to scrape videos off the internet and call different APIs, we had to make sure that the videos we used had a Creative Commons License. A Creative Commons license allowed us to legally share other people's’ work, in this case being the sports highlights clips. In addition to that, we were able to request  sports score data from a company known as MySportsFeeds, and someone from the company personally reached out to us, giving us free access to use their service and allowed us to display that data. In addition to that, since there were many moving components, we made sure to always keep our project as a free service. We thought it was morally wrong to use other people's work to make money for ourselves. Lastly, since we did have a login and customization feature, we had to make sure that our users data was kept safe, which is why we opted to go with Google’s Firebase system. The service automatically encrypted our users passwords; therefore, no one could simply gain access to that. Fortunately, our project wasn’t dealing with very sensitive data nor any technology that could directly harm a user’s life, so our ethical considerations were thus limited.

\section{Economic}
\par As this was a web based project our goals can be reached through construction and design of code, which is a free resource. Also, because we currently hold student titles and our goals are not for profit, most services are offered at free or greatly reduced prices. Therefore, the current costs of our project totaled nothing. However, if we continue to improve the project post-graduation we may need to examine the services as we scale up server space and/or have a need for higher performing equipment, which will see the charges begin to add up . (Add line on how creative commons allows us free use of stuff) 

\section{Usability}
\par One of the main problems we were trying to address while working on our project was to make the service more user friendly by creating more continuity among different sport pages throughout the site. In our opinion, we definitely achieved that. Now users don’t need to get used to many different screens. In addition to that, we strived to limit the number of buttons on our website as well as create a large video player in the middle of the screen to keep videos playing at all times. When it came to modifying settings, we went with a visual approach so that the user could clearly see what he or she is selecting. Lastly, our entire application was built in different modules, and this allows us to easily adjust the site to make it mobile and tablet friendly!

\section{Lifelong Learning}
\par For our project we decided to challenge ourselves by tackling the problem using modern frameworks and technologies. This project has inspired us both to pursue further projects to improve our proficiency and expertise regarding these technologies. Because these technologies are relatively new there are less references available so this improved our ability to digest the given documentation to debug and understand our issues better. This was an important skill to have gained and cemented into our repertoire because it can be applied later on in life on future projects and developments. 